Solving an Exam Scheduling Problem Using a Genetic Algorithm

### 2009-12-02 Paper/paper.tex
Paper update

\section{Conclusion}
  \subsection{Fitness Function Modifications}
    The fitness function can be modified by any monotone function to obtain identical 
    results for the 3 non-GA methods, which only need to choose the better fitness 
    and do not use the fitness values in any important way. The GA, however, uses the 
    fitness values to decide the probability of schedules being selected and modified 
    for subsequent generations. Modifying the fitness function in a variety of ways 
    (perhaps calculating the total penalty that a schedule gets instead averaging over 
    the values given by each student and room) might improve the quality of the GA 
    approach to this problem. The fitness function used here could be modified in many 
    ways, and investigating this would be very interesting.

>>>>

\section{Conclusion}
  Any monotone function can be applied to the fitness values to obtain identical 
  results for the 3 non-GA methods, which only need to choose the better fitness 
  and do not use the fitness values in any important way. The GA, however, uses 
  the fitness values to decide the probability of schedules being selected and 
  modified for subsequent generations. It might be possible to reduce or increase 
  the probability of poor functions being selected for mutation or crossover.

  Modifying the fitness function in a variety of ways (perhaps calculating the 
  total penalty that a schedule gets instead averaging over the values given by 
  each student and room) might improve the  quality of the GA approach to this 
  problem. The fitness function used here could  be modified in many ways, and 
  investigating this would be very interesting.

  Unfortunately, without further investigation and modification, the GA given 
  should not be used. Perhaps a novel form for representing schedules could make 
  a GA approach for this problem perform better than mutate search. We recommend 
  Mutate search for solving problems of this type. A typical PC can generate a 
  relatively good schedule for a large exam scheduling problem overnight using the
  mutate search method. Mutate search is very easy to implement, making it even 
  more attractive.

  Mutate search can be modified to change the rate of mutation and number of attempts 
  at each step, which suggests that much better methods can be developed based on the 
  it. This could be an interesting direction for further research.
